---
title: "Lab 9 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

```{r}
library(tidyverse)
library(naniar)
library(janitor)
library(here)
```

## Seating
1. If you already have a group, it will be helpful to start sitting next to each other.
2. If you don't have a group, hang tight we are working on it.
3. Please setup your computer as normal for today.

## Warm-up
1. In the data folder there is an epidemiology data set on an outbreak of malaria.
```{r}
epidemiology <- read_csv(here("data","malaria.csv"))
epidemiology
```

2. `rdt` refers to rapid diagnostic test and they are identified here by age group.
```{r}
epidemiology[,7:8]
```

3. Make the data tidy and store them as a new object.
```{r}
epidem_tidy <- epidemiology %>% 
  janitor::clean_names() %>% 
  pivot_longer(cols=starts_with("malaria_rdt"),
               names_to = "malarial_age",
               values_to = "cases") 
epidem_tidy
```

4. Which district had the highest *total* number of cases on July 30, 2020?
```{r}
epidem_tidy %>% 
  filter(data_date == "2020-7-30") %>% 
  group_by(district) %>% 
  slice_max(cases)
```

