---
title: "Lab 13 Homework"
author: "Please Add Your Name Here"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: spacelab
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Answer the following questions and complete the exercises in RMarkdown. Please embed all of your code and push your final work to your repository. Your final lab report should be organized, clean, and run free from errors. Remember, you must remove the `#` for the included code chunks to run. Be sure to add your name to the author header above. For any included plots, make sure they are clearly labeled. You are free to use any plot type that you feel best communicates the results of your analysis.  

Make sure to use the formatting conventions of RMarkdown to make your report neat and clean!  

## Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(shiny)
library(shinydashboard)
library(here)
library(RColorBrewer)
```

## Wolves practice from 12-2
1. Start by loading and exploring the data.
```{r}
wolves <- read_csv("data/wolves_data/wolves_dataset.csv")
```

```{r}
names(wolves)
```

2. For the app, here is a faceted version of what we are looking for. We want the reactive part to be `pop` and you should use `shinydashboard`.
```{r}
wolves %>% 
  filter(sex!="NA") %>% 
  ggplot(aes(x=sex, fill=sex))+
  geom_bar()+
  facet_wrap(~pop)
```

```{r}
ui <- dashboardPage(skin = "purple",
  dashboardHeader(title = "Wolves"),
  dashboardSidebar(disable = T),
  dashboardBody(
    fluidRow(
      box(title = "Plot Options", width = 3,
        selectInput("x", "Select Wolf Population", choices = unique(wolves$pop))
      ), # close the first box
      box(title = "Plot of Wolves Data", width = 8,
        plotOutput("plot", width = "600px", height = "500px")
      ) # close the second box
    ) # close the row
  ) # close the dashboard body
) # close the ui

server <- function(input, output, session) { 
  output$plot <- renderPlot({
  ggplot(filter(wolves,pop==input$x & sex!="NA"), aes(x=sex, fill=sex)) +
      geom_bar() + 
      theme_classic(base_size = 18) +
      scale_fill_brewer(palette = "RdPu")
  })
  session$onSessionEnded(stopApp)
  }

shinyApp(ui, server)
```

## Push your final code to GitHub!
Please be sure that you check the `keep md` file in the knit preferences. 