---
title: "Lab 4 Warm-up"
output: html_document
date: "2023-01-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. In a new R Markdown document, load the tidyverse and a package called `palmerpenguins`.
```{r message=FALSE, warning=FALSE}
library("tidyverse")
library("palmerpenguins")
```

## 2. What are the dimensions of the dataset `penguins`?
```{r}
dim(penguins)
```
The dimensions are 344 rows by 8 columns.

## 3. What are the names of the variables in the `penguins` dataset?
```{r}
names(penguins)
```

## 4. How many individuals were sampled on each island in the `penguins` dataset?
```{r}
sum(penguins[,2] == "Biscoe")
sum(penguins[,2] == "Dream")
sum(penguins[,2] == "Torgersen")
```
In summary, 168 penguins from Biscoe, 124 penguins from Dream, and 52 penguins from Torgersen.

## 5. What is the mean body mass for all individuals in the `penguins` dataset?
```{r}
colMeans(penguins[,6],na.rm=TRUE)
```
The mean body mass is 4200g, or 4.20kg.

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
